\documentclass[10pt]{moderncv}
\moderncvstyle{classic} % optional argument are 'nocolor' and 'roman'
\usepackage[applemac]{inputenc}

\newcommand*{\up}[1]{\textsuperscript{#1}}

%\usepackage[latin1]{inputenc}   % character encoding

% personal data
\firstname{Pawel}
\familyname{Kowalski}
\title{Curriculum Vit\ae{}} 
% \address{Tellstrasse 8\\3014 Bern}
\phone{+41/79 436 14 02}
\email{pkowalski@mila.com}
% \extrainfo{\weblink{https://orbit7.ch}}
% \quote{}

\begin{document}
\maketitle
\makequote

\section{Profile}
\cvitem{}{I'm a poly-skilled software engineer with over 15 years of industry experience in building 
and running software systems small and large. I've spent over 8 years in technical leadership 
roles and have a track record of building high-performing teams and delivering strategic projects. 
My passion is the design and implementation of digital products.}


\section{Areas of Expertise}
\cvitem{Leadership}{Able to drive technical, systemic and cultural change, influence without requiring 
authority and build high-performing engineering teams.}

\cvitem{Technology}{Broad and deep experience with many tools and technologies related to building and 
running high-traffic distributed systems.}

\cvitem{Methods}{Strong foundations in agile, lean thinking, design sprints and continuous delivery with 
track record of architecting large cloud-native applications.}

\cvitem{Languages}{Python, Javascript, Java}


\section{Career History}
\workitem{Dec 2018--Present}
{CTO, Mila AG, Zurich, Switzerland}
{Responsible for the interdisciplinary Product and Engineering Team at Mila AG}


\workitem{Apr 2018--Dec 2018}
{Co-Founder orbit7 gmbh, Bern, Switzerland}
{Co-founded orbit7 gmbh, a boutique software engineering company focused on building digital products 
and providing specialized engineering services for companies in the areas of data analysis, search 
technologies and prototyping.}

\workitem{}
{Software Engineering - Bernmobil}
{Designed a library to process massive amounts of data for public transportation to detect anomalies 
and for monitoring of public means of transportation.}

\workitem{}
{Product design and development - Lernpfad.ch}
{Designed and implemented lernpfad.ch in collaboration with LerNetz AG, https://lernpfad.ch}


\workitem{Feb 2011--Apr 2018}
{Co-Founder Iterativ gmbh, Bern, Switzerland}
{Co-founded Iterativ GmbH, a boutique software engineering company specialised in developing digital 
products and software for new business ideas. Project acquisition and management of the company 
with an interdisciplinary team of 7 engineers and UX specialists building software for large Swiss 
companies like Swisscom, ABB, Switch.}

\workitem{}
{Technical and Product Lead - MySkillBox, HEP Verlag}
{Designed and implemented the MySkillBox digital learning and publishing environment for swiss 
schools using the Design Sprint Methodology - https://myskillbox.ch/}

\workitem{}
{Technical and Product Lead - Helloclass.ch, Swisscom AG}
{Designed and implemented the helloclass class management tool. helloclass is used in schools in 
every canton in switzerland to manage class assignments and schedules - https://helloclass.ch}

\workitem{}
{Project Management and Tech Lead - MyService, Swisscom AG}
{Lead the implementation of the business critical MyService case management tool for the MyService 
offering by Swisscom. \smallpara https://www.swisscom.ch/en/residential/services/myservice.html}


\workitem{Feb 2011--Jun 2011}
{Senior Software Engineer, AdNovum AG, Bern, Switzerland}
{Performance analysis, design and implementation of improvements in the visa issuance system of 
the Federal Administration.}


\workitem{Apr 2009--Jul 2010}  
{Application Engineer, UBS AG, Zurich, Switzerland}
{ISToolset portfolio management project (UBS Top 50 application): 
Analysis, design and implementation of a core component for business case data processing (approx. 
500'000 business cases per day). In addition, technical management of the involved specialists 
(DB, Business, Testing).}


\workitem{Oct 2008--Apr 2009}
{MSc Project, ETH Zurich, Systems Group}
{Modularization of the Apache Derby database management system.
The goal of the project is to split the Apache Derby database software into several independent 
and distributed components to improve scalability and configurability. Used technologies: OSGi, R-OSGi}


\workitem{Jan 2005--Sep 2008}
{Application Engineer, UBS AG, Zurich, Switzerland}
{ISToolset portfolio management project (UBS Top 50 application):
Collaboration in the analysis, design and development of the newly implemented ordering system. 
The goal of this project was to provide a general infrastructure for the parallelization of computationally 
intensive tasks and their load balancing over several distributed servers.}


\section{Other Activities}

\cvitem{Feb 2004--Jul 2004}
{Internship, INRIA Institut National de la Recherche en Informatique et en Automatique, Sophia Antipolis, France}

\cvitem{Oct 2002--Jul 2003}
{Internship, ELCA Informatik AG, Bern, Development of a software architecture analysis tool - http://dptool.sf.net}


\section{Education}
\eduitem{Sep 2006--Apr 2009}
{MSc ETH in Computer Science, Specialization Information Systems}
{ETH Zurich, Department of Computer Science, Zurich}

\eduitem{Oct 2000--Jan 2005}
{BSc, Computer Science and Software Engineering}
{Berne University of Applied Sciences, School of Engineering and IT, Biel, Switzerland}

\eduitem{Oct 2003--Jul 2004}
{Erasmus Exchange Year, Software Engineering, Specialization Distributed Systems}
{Universit\'e de Nice Sophia Antipolis, Ecole Sup\'erieure en Sciences Informatiques, France}


\section{Sprachen}
\cvitem{}{\textbf{Deutsch} - First language}{}
\cvitem{}{\textbf{Englisch} - Proficient}{}
\cvitem{}{\textbf{French} - Proficient}{}


\end{document}
